---
title: "Data Exploratory Analysis"
author: "AAA"
date: "20 de diciembre de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Course Description

When your dataset is represented as a table or a database, it's difficult to observe much about it beyond its size and the types of variables it contains. In this course, you'll learn how to use graphical and numerical techniques to begin uncovering the structure of your data. Which variables suggest interesting relationships? Which observations are unusual? By the end of the course, you'll be able to answer these questions and more, while generating graphics that are both insightful and beautiful.

1

## Exploring Categorical Data

In this chapter, you will learn how to create graphical and numerical summaries of two categorical variables.


### Contingency table review

In this chapter you'll continue working with the comics dataset introduced in the video. This is a collection of characteristics on all of the superheroes created by Marvel and DC comics in the last 80 years.

Let's start by creating a contingency table, which is a useful way to represent the total counts of observations that fall into each combination of the levels of categorical variables.

### INSTRUCTIONS

The dataset has been loaded into your workspace as comics.

Type the name of the dataset to look at the rows and columns of the dataset.
View the levels() that the align variable can take.
View the levels() that the gender variable can take.
Create a contingency table of the same two variables.

```{r}
#pre exercise code


url <- "http://s3.amazonaws.com/assets.datacamp.com/production/course_1796/datasets/comics.csv"

#download.file(url, "comics.csv")
#install.packages("dplyr")

#dataframe
comics <- read.csv("comics.csv", stringsAsFactors = TRUE)
```

```{r}
# Print the first rows of the data
comics

# Check levels of align
levels(comics$align)

# Check the levels of gender
levels(comics$gender)

# Create a 2-way contingency table
table(comics$align, comics$gender)
```

```{r}

```

```{r}

```

```{r}

```




## Exploring Numerical Data

In this chapter, you will learn how to graphically summarize numerical data.


```{r}

```

```{r}

```

```{r}

```

```{r}

```



## Numerical Summaries

Now that we've looked at exploring categorical and numerical data, you'll learn some useful statistics for describing distributions of data.


```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```




Case Study

Apply what you've learned to explore and summarize a real world dataset in this case study of email spam.

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```





